\section{Introduction}
Editor: S. Ritz

(1-2 pages)

Includes connections to other papers, starting with the Overview paper, and the LSST observatory system.

Starting point is LCA-11591, the Camera Final Design Report.

\section{Requirements and Design Overview}
Editor: S. Ritz

(5-10 pages)

\subsection{Summary of requirements}
\subsubsection{Details of Camera requirements related to science performance}
\subsubsection{Summary of functional and related requirements}
\subsubsection{Additional requirements}
Mechanical, etc, will just be listed.
\subsection{Overview of Design}
...which will lead directly into the rest of the sections. We will likely follow the path of the light through the Camera.

\section{Optics}
Editors: S. Ritz and J. Wolfe

(8 pages)

\subsection{Refractive Optics}
\subsection{Filters}
\subsubsection{Filter performance}

\section{Camera Body and Mechanisms}
Editors: S. Ritz and M. Nordby 
Camera body intro and overview.

\subsection{Filter Exchange System}
Editors: P. Antilogous and P. Karst
(5 pages)

\subsection{Shutter}
Editors: M. Oriunno, M. Nordby
(2 pages)

\section{Cryostat}
Editors: M. Nordby
Overview.
\subsection{Cryostat mechanical design and implementation}
\subsection{Vacuum system}
\subsection{Refrigeration and thermal control}
Editor: R. Schindler, will summarize the larger refrigeration system paper here.
(4 pages)
\subsection{Utility trunk}
Editor: M. Nordby

\section{Focal Plane}
There is a separate science rafts and corner rafts paper, so key points only will be summarized here.
Editors: C. Stubbs

(8 pages)

\subsection{Science Rafts}
\subsubsection{Sensors}
\subsubsection{Electronics}
\subsection{Corner rafts}

\section{Camera Control System and Data Acquisition}
Editors: A. Johnson, M. Huffer, G. Thayer
Includes data flow, control, and telemetry.
(5 pages)

\section{Integration and Test}
Editors: A. Roodman and T. Bond
(15-20 pages)
\subsection{Integration flow and tooling}
\subsection{Challenges}
\subsection{Results}
A long section...
\subsection{Operational constraints}

\section{On-summit operations}
Editor: M. Nordby
Includes in-situ thermal environment control, capabilities for servicing, 

\section{Summary}
Editor: S. Ritz
